Complex Analysis of Askaryan Radiation: Towards UHE-$\nu$ energy Reconstruction via the Hilbert Envelope of Observed Signals

### 2025-02-01 template.tex
big update, with potential final result

\documentclass[amsmath,amssymb,aps,prd,10pt,twocolumn,showkeys]{revtex4}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{empheq}
\usepackage{siunitx}
\DeclareMathOperator\erfc{erfc}
\DeclareMathOperator\erf{erf}
\DeclareMathOperator{\sgn}{sgn}
\begin{document}

@@

r(t) &= R_0 e^{-\gamma t} \cos(2\pi j f_0 t) \\

@@

\item Note that $I(x,0)$ has exact solutions:

@@

I(x,0) &= \frac{\sqrt{\pi}}{2}(1+\erf(jx)) \\
I(x,0) &= \frac{\sqrt{\pi}}{2} + j e^{x^2} D(x)

@@

However, approximating $I(x,z_0) \approx I(x,0)$ drops the dependance on $\gamma$ and $f_0$.
\item To solve Eq. \ref{eq:end2}, the integral function is expanded in powers of $z_0$.  This is wise, given that the UHE-$\nu$ signal bandwidth will usually exceed that of a dipole receiver with response $r(t)$ and analytic signal $r_a(t)$.

>>>>

\documentclass[amsmath,amssymb,aps,prd,10pt,twocolumn,showkeys]{revtex4}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{empheq}
\DeclareMathOperator\erfc{erfc}
\DeclareMathOperator\erf{erf}
\DeclareMathOperator{\sgn}{sgn}
\begin{document}

@@

@@

\item The solution for $I(x,z_0)$ in Eq. \ref{eq:end2} may be found using contour integration, and comparison with standard results from integral tables.  First, $z$ is substituted for $(x+jy)$:

@@

z &= x+jy \\
dz &= j dy \\
y &= j(x-z)

@@

Let $z_1 = x+jz_0$. The substitution changes $I(x,z_0)$ into
I(x,z_0) = -j \int_{x}^{x+jR} \frac{(z-x)}{(z-z_1)} e^{z^2} dz
First, assume that $x>0$ and $x>\Im \lbrace z_0\rbrace$ so that the pole is in the first quadrant.  Define four line integrals to enclose the pole, $I_1$ through $I_4$.  First, $I_1$ extends from $x$ to $x+jR$, and is equal to $I$:
I_1 &= -j \int_{x}^{x+jR} \frac{(x+jy-x)}{(x+jy-(x+jz_0))} e^{(x+jy)^2} j dy \\
I_1 &= \int_0^{\infty} \frac{y e^{(x+jy)^2}}{y-z_0} dy = I(x,z_0)
Regarding the limits, $z = x$ corresponds to $y=0$, and $z = x+jR$ corresponds to $y=R$, where $R \to \infty$.  The line integral $I_2$ runs from $x+jR$ to $jR$.  The numerator goes as $\exp(z^2) \propto \exp(-R^2)$.  For $R \to \infty$, $I_2$ vanishes.  The line integral $I_3$ returns from $jR$ to $0$.  The integrand is parametrized by $z = jy$, $dz = jdy$.  Along $I_3$, $x = 0$.  The result is
I_3 = -\int_0^{R} \frac{ye^{-y^2}dy}{y-z_0}
The line integral $I_4$ finishes the loop, with limits $0$ and $x$.  However, the numerator of the integrand is proportional to $(z-x)$. Since the parameterization is $z=x$, the integrand vanishes.  Thus, only $I_1$ ane $I_3$ remain in the sum of line integrals, which enclose the pole at $z_1$.  The contour integral is therefore:
\oint \frac{-j(z-x)e^{z^2}dz}{(z-z_1)} = I(x,z_0) + I_3
According to the Cauchy integral formula, the left-hand side is $2\pi j$ times the residue at $z_1$:
\oint \frac{-j(z-x)e^{z^2}dz}{(z-z_1)} = 2\pi j z_0 e^{(x+jz_0)^2}
Solving for $I(x,z_0)$:
I(x,z_0) = 2\pi j z_0 e^{(x+jz_0)^2} + \int_0^{\infty} \frac{ye^{-y^2}dy}{y-z_0}
The term originating from $I_3$ may be found in standard integral tables.  The result is 
\boxed{
I(x,z_0) = 2\pi j z_0 e^{(x+jz_0)^2} + \frac{\pi}{2}e^{z_0^2}\erfc(z_0)}
The final result for $\mathcal{E}_{r * s}$ is
\mathcal{E}_{r * s} = \frac{1}{2}| r_a(t) * s_a(t)| = R_0 E_0 \sigma_t^2 e^{-x^2} \left|\frac{I(x,z_0)}{\sqrt{\pi}}\right|
